---
output: rmarkdown::github_document
---

`zkcmd` : Tools to Administer 'Zookeeper' Instances with Four-letter Commands

'Zookeeper' enables super-easy multi-node configuration management for distributed
computing. The 'Zookeeper' instances themselves can be managed by issuing "four-letter
words" over a TCP socket connection.. Methods are provided to interface with this
administrative API.

The following functions are implemented inside the `zmckd` reference class:

- `available_commands()`: Show available four-letter commands
- `conf()`: Print details about serving configuration.
- `connect(host = "localhost", port = 2181L, timeout = 30L)`: Connect to a Zookeeper instance.
- `cons()`: List full connection/session details for all clients connected to this server.
- `crst()`: Reset connection/session statistics for all conn
- `dirs()`: Shows the total size of snapshot and log files in bytes
- `dump()`: Lists the outstanding sessions and ephemeral nodes. This only works on the leader.
- `envi()`: Print details about serving environment.
- `gtmk()`: Gets the current trace mask as a 64-bit signed long value in decimal format.
- `initialize(..., host = "localhost", port = 2181L, timeout = 30L)`: Initialize a new Zookeeper commander object.
- `isro()`: Tests if server is running in read-only mode.
- `ruok()`: Tests if server is running in a non-error state. The server will respond with imok if it is running. Otherwise it will not respond at all.
- `send_cmd(cmd)`: Issue a four-letter command. Used internally but can also be used to take advantage of new commands before a package update.
- `srst()`: Reset server statistics.
- `srvr()`: Lists full details for the server.
- `stat()`: Lists brief details for the server and connected clients.
- `wchc()`: Lists detailed information on watches for the server, by session.
- `wchp()`: Lists detailed information on watches for the server, by path.
- `wchs()`: Lists brief information on watches for the server.

### Installation

```{r eval=FALSE}
devtools::install_git("https://gitlab.com/hrbrmstr/zkcmd.git")
```

```{r message=FALSE, warning=FALSE, error=FALSE}
options(width=120)
```

### Usage

```{r message=FALSE, warning=FALSE, error=FALSE}
library(zkcmd)

# current verison
packageVersion("zkcmd")

zk <- zkcmd$new()

zk$ruok()

str(zk$srvr())

str(zk$conf())

zk$isro()

zk$cons()

```

### Test Results

```{r message=FALSE, warning=FALSE, error=FALSE}
library(zkcmd)
library(testthat)

date()

test_dir("tests/")
```

